Papers

### 2022-12-28 quarto/index.qmd
update

<img src="img/aston.jpg"  border="0" vspace="10" hspace="0" /><br>
<img src="img/email.png" height="30" width="200" vspace="0" ><br>

@@

## [All Papers](papers.qmd)

@@

* Area Chair
	* Annual Meeting of the Association for Computational Linguistics (**ACL**)
	* Conference on Empirical Methods in Natural Language Processing (**EMNLP**)

* Senior Program Committee
	* AAAI Conference on Artificial Intelligence (**AAAI**)

* Journal Editorial Board
	* Frontiers in Big Data

>>>>

<img src="img/aston.jpg"  border="0" vspace="10" hspace="0" class="bio-photo"><br>
<img src="img/email.png" height="30" width="200" vspace="0" ><br>

@@

## All Papers

[List](papers.qmd)

@@

* Area Chair
	* *Annual Meeting of the Association for Computational Linguistics* (**ACL**)
	* *Conference on Empirical Methods in Natural Language Processing* (**EMNLP**)

* Senior Program Committee
	* *AAAI Conference on Artificial Intelligence* (**AAAI**)

* Journal Editorial Board
	* *Frontiers in Big Data*
